---
title: "p8105_hw5_zf2212"
author: "Catherine"
date: "11/2/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 10,
  fig.asp = .6,
  out.width = "90%"
)
library(tidyverse)
library(purrr)
library(stringr)
```

### Problem 1

This problem is based on the data from a longitudinal study that included a control arm and an experimental arm. Data for each participant is included in a separate file, and file names include the subject ID and arm.

#### 1.1

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time.

```{r study data import, message = FALSE}
# creat file names list with path
file_list = tibble(
  file_name = list.files(path = "./data")) %>% 
  mutate(path = str_c("./data/", file_name)) # rename the variable

# read in data and tidy
data_raw = file_list %>% 
  mutate(path, path = map(path, read_csv)) %>% # map and save the result
  unnest() 
data_tidy = data_raw %>% 
  separate(file_name, into = c("arm", "id"), sep = "_") %>% 
  mutate(arm, arm = recode(arm, 
                           con = "control",
                           exp = "experimental"), # make values clear
         id = str_replace(id, ".csv", "")) %>% 
  select(id, arm, everything())

# skimr::skim(data_tidy)
```
__Description__

There are `r nrow(data_tidy)` observations and `r ncol(data_tidy)` columns in the dataset and no missing values. __Variables__ include `r names(data_tidy)`. Other than `id` and `arm`, all variables are class `numeric`. 

#### 1.2

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r spaghetti plot, fig.width = 9}
# prepare the data
data_plot = data_tidy %>% 
  gather(key = "week", value = "observation", week_1:week_8) %>% # gather the data for plot
  mutate(week, week = as.numeric(str_replace(week, "week_",""))) # convert week into number
# make the plot
data_plot %>% 
  ggplot(aes(x = week, y = observation, color = id)) +
  geom_point(alpha = .6, size = .8) +
  geom_line(alpha = .6) +
  stat_summary(fun.y = mean, color = "black", 
               position = position_dodge(0.75),
               geom = "line",
               size = .8,
               alpha = .6) +
  facet_grid(~arm) + 
  scale_x_discrete(limits = c(1:8)) + # break in 8 weeks
  labs(title = "Spaghetti Plot of Control and Experimental Arms",
       x = "Week",
       y = "Observation",
       caption = "The black lines show the mean of each group") +
  theme_bw() + # set names and themes
  theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5, face = 'bold')) +
  guides(col = guide_legend(nrow = 1))
```

__Comment__

There is a growing trend for participants in the experimental group over 8 weeks of study. 

There is no significant trend for participants in the control group.

Most of the participants in the control group were observed lower values compared to experimental group.

### Problem 2
This problem is based on the data gathered by The Washington Post about homicides in 50 large U.S. cities over the past decade.

#### 2.1 

Describe the raw data. Create a city_state variable and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides.

```{r homicides data import, results = "hide"}
# import data 
homicide_raw = read_csv("./data_homicides/homicide_data.csv", col_types = "cccccccccddc")
# look at the raw dataset
str(homicide_raw)
```
__Description__

The raw data includes `r nrow(homicide_raw)` observations and `r ncol(homicide_raw)` variables.
The dataset includes the information of `r nrow(homicide_raw)` criminal homicides cases over the past decade in `r nrow(distinct(homicide_raw, city, state))` distincts cities. __Variables__ include `r names(homicide_raw)`. Other than `lat` and `lon`, all variables are class `character`. `victim_race` includes `r homicide_raw %>% select(victim_race) %>% distinct %>% count` distinct races. `disposition` includes `r homicide_raw %>% select(disposition) %>% distinct %>% count` kinds of disposition for cases.

```{r new variable and sum}
# create new variable
homicide_data = homicide_raw %>% 
  mutate(city_state = str_c(city,state, sep = ", ")) %>% 
  select(uid, reported_date, city_state, everything()) 
# summarize the homicide data
homicide_sum = homicide_data %>% 
  group_by(city_state) %>% 
  summarize(total_homicides = n(),
            total_unsolved = sum(disposition %in% c("Closed without arrest", "Open/No arrest")))
```

#### 2.2

Estimate the proportion of homicides that are unsolved for the city of Baltimore, MD

```{r baltimore}
# filter the baltimore data
bal_data = homicide_sum %>% 
  filter(city_state == "Baltimore, MD")
# prop test for baltimore
tb_bal = prop.test(bal_data$total_unsolved, bal_data$total_homicides) %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high) # pull estimated proportion and CI
knitr::kable(tb_bal)
```

For the city of __Baltimore, MD__, the estimated proportion is `r tb_bal$estimate`, the confidence intervals is (`r tb_bal$conf.low`, `r tb_bal$conf.high`).

#### 2.3

Extract both the proportion of unsolved homicides and the confidence interval for all cities. 

```{r prop function}
city_prop_test = function(x, n) {
  prop.test(x, n) %>% 
    broom::tidy() %>% 
    select(estimate, conf.low, conf.high) %>% 
    round(3)
    
}
```
```{r prop test for all cities}
city_prop = homicide_sum %>% 
  # map the data by the function
  mutate(prop = map2(.x = total_unsolved, .y = total_homicides, ~city_prop_test(.x, .y))) %>% 
  unnest() %>% 
  select(city_state, estimate, conf.low, conf.high)
knitr::kable(city_prop)

```

#### 2.4
Create a plot that shows the estimates and CIs for each city. Organize cities according to the proportion of unsolved homicides.

```{r city plot, fig.width = 9}
city_prop %>% 
  # organize the city according to proportion
  mutate(city_state = forcats::fct_reorder(city_state, estimate, .desc = T)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point(color = "red") + # plot the estimate
  geom_errorbar(aes(x = city_state, ymin = conf.low, ymax = conf.high)) + # plot the intervals
  theme(axis.text.x = element_text(angle = 90), plot.title = element_text(hjust = 0.5, face = 'bold')) +
  labs(title = "Estimates and CIs of the Unsolved Homicides Proportion in 50 American Cities",
       x = "City",
       y = "Proportion",
       caption = "Data from The Washington Post") 
```

The plot shows the estimates and CIs for 51 American cities. Most of the cities hava an unsolved homicide proportion over 25%. It reflects the problem that there are many areas across the country where murder is common but arrests are rare.


